---
title: "farsFiki"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{farsFiki}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(farsFiki)
```

## fars_read function

This function extracts a database from a .csv file and turns it into a tibble, ignoring all simple diagnostic messages and not showing any progress bar. If the file named in the argument doesn't exist, it will
generate an error and this message will be printed: *"file 'filename' does not exist"*.

The class of the resulting object is **tbl_df**.

## make_filename function

This function creates a filename with this format: "accident_*aaaa*.csv.bz2" indicating a year instead of *aaaa*. The value for *aaaa* comes from the function's argument.

It works with any numeric value for year. If we enter a non-integer value as an input, the function uses only the integer part of the number.

## fars_read_years function

This function evaluates if the elements of a vector called "years" correspond to the years that appear in the names of the files with the format "accident_*aaaa*.csv.bz2" where *aaaa* is the year and returns a list of data frames containing years and months from each file.

If a year doesn't appears in any filename, it will return a warning: "invalid year: **year that is not in any filename**".

## fars_summarize_years function

This function creates a table that summarize the number of observation in every file with the format "accident_*aaaa*.csv.bz2" where *aaaa* is a year.
The output is a table where each row is a month and each column is a year, and contains the number of observations for each month and year in the files with the mentioned format

If a year doesn't appears in any filename, it will return a warning, as in **fars_read_years** function.

## fars_map_state function

This function creates a map with the accidents happened in a certain year in a selected state.

The arguments for this function are a code for a state and a year.

The output is a map of the selected state with points corresponding to theplaces where the accidents occurred in the selected year.

If state.num doesn't correspond to a state code, the process stops. If in the selected year and state there were no accidents, a message is shown: "no accidents to plot".
